\chapter{Progress Report}
My aim is to tackle the problem of AI-based mathematical discovery via a hybrid, two-pronged approach; building theory by examining the nature of mathematical discovery and working on targeted applications.
As summarized in the preceeding chapters, I would like to roughly organize my PhD thesis into the following components:
\begin{itemize}
    \item \textbf{Theory}:
        \subitem \textit{The nature of mathematical discovery, particularly in the age of AI}
        \subitem \textit{``Interestingness'' and the conjecture space}
        \subitem \textit{Multi-agent system based mathematical discovery}
    \item \textbf{Applications}:
        \subitem \textit{Domain specific applications: Holographic entropy inequalities, $\text{WAM}(n,s)$ and the $\text{abc}$-conjecture}
        \subitem \textit{Conjectures as sub-goals in proof formalization} 
\end{itemize}
In the remainder of this chapter, I will describe the current status of these projects along with the future plan and a timeline for the completion of the PhD.

\section{Current Work}

\section{Future Plan}
\subsection{``Interestingness'' and the conjecture space}
The first line of action is to grade conjectures based on a reasonable notion of `interestingness'. Once this is implemented, the goal is to publish a package. This would allow domain experts across different mathemtical fields to generate conjectures, hopefully leading to collaborations and new discoveries.
This would also give valuable data to judge the effectiveness of the chosen `interestingness' heuristic. There are a number of different heuristics possible (as described in the corresponding chapter) but the initial focus will be on `information content'.
\\\\
I

\section{Timeline}

\begin{longtable}{|c|c|c|c|}
\hline
\thead{\textbf{Year}} &\thead{\textbf{Michaelmas}} & \thead{\textbf{Lent}} & \thead{\textbf{Easter}} \\
\hline
2 & \makecell[l]{Finish article on \\(article name) and\\ submit for publication. \\\\ Continue work on incorporating\\ conjectures as sub-lemmas in \\formal theorem proving.\\ Submit for publication. \\\\ Implement \& grade conjectures\\based on our notion of-\\ ``information content''. \\\\ Explore properties of \\$\text{WAM(n,s)}$ with the aim\\ to form conjectures.} 
    & \makecell[l]{Begin work on \\``agent''-based\\ math discovery\\\\Work on package\\ for conjecture\\space codebase.\\\\Begin writing up \\$\text{WAM(n,s)}$ results\\\\Continue exploring model \\ theory connections}
        & \makecell[l]{Test proof-of-concept\\on ``agent''-based\\system.\\\\Publish package\\on conjecture \\space codebase.\\\\Hopefully incorporate \\model theory\\connections\\\\Finish initial \\report on $\text{WAM(n,s)}$}\\
\hline
3 & \makecell[l]{Work on different\\interestingness heuristics.\\Dedicated agents with\\decision policies based\\ on these heuristics.\\\\ Wrap-up project on $\text{WAM(n,s)}$\\ and begin work on follow-ups} & \makecell[l]{Discovering new\\conjectures with\\multi-agent systems.\\\\Follow-ups to\\previous applications\\and theoretical insights.} & \makecell[l]{Prepare previous\\projects for publication}\\
\hline
4 & \multicolumn{3}{|c|}{Write a comprehensive thesis and finish any ongoing publications } \\
\hline
\end{longtable}



